---
title: "MIS 381N - Stochastic Control and Optimization Project 5"
author: 'Jushira Thelakkat, Zhiyi(Claire) Yang, Jiayan (Will) Lu, Sidhaarthan Velur
  Gopalakrishnan '
date: "April 25, 2018"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE}
rm(list=ls())
library(MASS)
library(ggplot2)
load('queue.rdata')
```

# Question 1

Use the function "fitdistr" in the R package MASS, to find the right parameters for inter-arrival and service time distributions. Try Gamma, Exponential and the Weibull distributions. Please use qqplots to to show the goodness of fits.

```{r,warning=FALSE}
# Calculating Inter-Arrival TIme
IA <- diff(A)

# Fit distributions for Inter-Arrival Time
e_fit_i <- fitdistr(IA, "exponential")
g_fit_i <- fitdistr(IA, "gamma")
w_fit_i <- fitdistr(IA, "weibull")

# Fit distributions for Service Time
e_fit_s <- fitdistr(S, "exponential")
g_fit_s <- fitdistr(S, "gamma")
w_fit_s <- fitdistr(S, "weibull")

# Convert variables to a dataframe
service_arrival <- data.frame(S,A)
inter_arrival <- data.frame(IA)

# QQ-Plot for Inter-Arrival Time
ggplot(inter_arrival, aes(sample = IA)) +
  stat_qq(distribution = qexp, 
          dparams = list(e_fit_i$estimate[1]), 
          geom = "line",
          aes(color = "exponential")) +
  stat_qq(distribution = qgamma, 
          dparams = list(g_fit_i$estimate[1], g_fit_i$estimate[2]), 
          geom = "line",
          aes(color = "gamma")) +
  stat_qq(distribution = qweibull, 
          dparams = list(w_fit_i$estimate[1], w_fit_i$estimate[2]), 
          geom = "line",
          aes(color = "Weibull")) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  scale_color_manual(name = "", 
                     values = c("exponential" = "black",
                                "gamma" = "green",
                                "Weibull" = "red"),
                     breaks = c("exponential",
                                "gamma",
                                "Weibull")) +
  labs(title = "Q-Q Plot for Inter-Arrival Time")

# QQ-Plot for Service Time
ggplot(service_arrival, aes(sample = S)) +
  stat_qq(distribution = qexp, 
          dparams = list(e_fit_s$estimate[1]), 
          geom = "line",
          aes(color = "exponential")) +
  stat_qq(distribution = qgamma, 
          dparams = list(g_fit_s$estimate[1], g_fit_s$estimate[2]), 
          geom = "line",
          aes(color = "gamma")) +
  stat_qq(distribution = qweibull, 
          dparams = list(w_fit_s$estimate[1], w_fit_s$estimate[2]), 
          geom = "line",
          aes(color = "Weibull")) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  scale_color_manual(name = "", 
                     values = c("exponential" = "black",
                                "gamma" = "green",
                                "Weibull" = "red"),
                     breaks = c("exponential",
                                "gamma",
                                "Weibull")) +
  labs(title = "Q-Q Plot for Service Time")
```

Looking at the Q-Q plot for both Inter-Arrival times and Customer Wait times, we can see that the gamma distribution is the closest to the actual distribution among weibull, exponential and gamma distribution

