---
title: "project5_g7_Q4"
author: "Group 7"
date: "April 25, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE}
rm(list=ls())
library(MASS)
library(ggplot2)
load('queue.rdata')
```

```{r}
# Calculating Inter-Arrival TIme
IA <- diff(A)

# Fit distributions for Inter-Arrival Time
g_fit_i <- fitdistr(IA, "gamma")

# Fit distributions for Service Time
g_fit_s <- fitdistr(S, "gamma")

```

# Question - 4

(Extra credit) Now we will consider the queuing configuration in 2 where each counter has its own queue, but arriving customers join the queue that has the shortest queue length. Use a simulation to find the optimal number of checkout counters to keep open in this configuration. What is the expected cost (pay + penalty)?

```{r,warning=FALSE}
# Assigning the number of simulations which refers to the number of customers walking into the store
N = 10000

# Vector to hold the cost with different counters
totalCost = rep(NA, 20) 

# Using gamma distribution to simulate the arrival and service times
for (i in 1:20) 
{
  gamma_inter = rgamma(n=N-1, shape=g_fit_i$estimate[1], rate=g_fit_i$estimate[2])
  gamma_arrival = c(0, cumsum(gamma_inter))
  gamma_service = rgamma(n=N, shape=g_fit_s$estimate[1], rate=g_fit_s$estimate[2])
  
  queueLength = rep(0,i) # length of queues for each of the counters
  D = rep(0,i) # service end times
  queueLength[1] = 1
  W = rep(NA,N)
  T = 0
  D[1] = T + gamma_service[1]
  W[1] = 0
  
  for (p in 2:N) 
  {
    queueLength[(D<=gamma_arrival[p]) & (queueLength!=0)] = queueLength[(D<=gamma_arrival[p]) & (queueLength!=0)] - 1 # if a customer arrives after the service end times of some counters, then queueLength decreases by 1
    x = which.min(queueLength) # customer chooses queue with shortest length
    queueLength[x] = queueLength[x]+1 # after customer joins the line, queueLength increases by 1
    T = max(D[x], gamma_arrival[p])
    old_D = D[x]
    D[x] = T + gamma_service[p]
    
    W[p] = max((old_D - gamma_arrival[p]),0)
    
  }
  totalCost[i] = sum(W > 10) + (max(D)/60 * 40 * i)
}


# Total cost for different counters
totalCost

# Plot the individual cost for different counters
plot(1:20, totalCost, type='line', xlab='# of Counters Open', ylab='Estimated Cost', main='Multiple Queues with Shortest Queue Selection')


# Minimum of the costs
min(totalCost)

# Counter configuration which has the lowest cost
which.min(totalCost)

# Mark the line in the plot
abline(v = which.min(totalCost) ,lwd=3, col="red")
```

The third scenario here is by far the most common situation that we face in grocery stores. There are multiple counters, and the customers join the queue which has the smallest number of customers. Solving for this method, we see that 13 is again the ideal number of counters which should be set up. This problem was solved by simulating for 10,000 customers.

