---
title: 'Project 1: Linear Programming'
author: "Brooks Beckelman"
date: "February 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(lpSolve)
```

## Function Inputs 

```{r}
#Liabilities 
liabilities = c(12000,18000,20000,20000,16000,15000,12000,10000)

#Bond prices
price = c(102,99,101,98,98,104,100,101,102,94)

#Coupons
coupons = c(5,3.5,5,3.5,4,9,6,8,9,7)

#Maturities
m = c(1,2,2,3,4,5,5,6,7,8)
```

## Q1. Formulate portfolio construction problem as a linear program. Clearly list and describe the decision variables, the objective, and all the constraints.

Decision Variables: Amount of each of the 10 bonds i.e. x1,...,x10

Objective: Minimize the total cost of the bonds 102x1 + 99x2 + 101x3 + 98x4 + 98x5 + 104x6 + 100x7 + 101x8 + 102x9 + 94x10

Constraints: cash flow inward from coupon and maturity payments must equal cash flow outward to liabilities for each year (1-8)

```{r}
# Objective
c = price

# Constraints
A = matrix(0,length(l),length(c))

for (i in seq_along(coup)){
  ## Fill matrix with coupon payments
  A[1:m[i]-1,i] = coup[i]
  ## Fill matrix with maturity payments and final coupon payments
  A[m[i],i] = 100 + coup[i]
}

## Direction Vector
dir = rep("=",length(l))

## Constraints Vector 
b = l
```

## 2. Test Case

```{r}
# Solve LP
s = lp("min",c,A,dir,b)
sol = s$solution

# Print Optimal Solution
for (i in seq_along(sol)){
  cat("Bond",i,"\t:\t",sol[i],"\n")
}
```