---
title: "MIS 381N - Project 1"
author: "Group 3 - Scroggings, Thelakkat, Tanwisuth, Wooten"
date: "February 13, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(lpSolve)
```

##Inputs 

```{r}
#Liabilities 
l = c(12000,18000,20000,20000,16000,15000,12000,10000)

#Bond prices
p = c(102,99,101,98,98,104,100,101,102,94)

#Coupons
coupons = c(5,3.5,5,3.5,4,9,6,8,9,7)

#Maturities
m = c(1,2,2,3,4,5,5,6,7,8)
```

## Q1. Formulate portfolio construction problem as a linear program. Clearly list and describe the decision variables, the objective, and all the constraints.

Decision Variables: Amount of each of the 10 bonds i.e. x1,...,x10

Objective: Minimize the total cost of the bonds 102x1 + 99x2 + 101x3 + 98x4 + 98x5 + 104x6 + 100x7 + 101x8 + 102x9 + 94x10

Constraints: cash flow inward from coupon and maturity payments must equal cash flow outward to liabilities for each year (1-8)

```{r}
#Objective
c = p

#Constraints
A = matrix(0,length(l),length(c))
for (i in seq_along(coupons)){
  A[1:m[i]-1,i] = coupons[i]
  #Matrix with maturity and coupon payments
  A[m[i],i] = 100 + coupons[i]
}

#Direction
dir = rep("=",length(l))

#Constraints Vector 
b = l
```

## Q2. Solving the test case

```{r}
#Solve LP
s = lp("min",c,A,dir,b)
sol = s$solution

#Optimal Solution
for (i in seq_along(sol)){
  cat("Bond",i,"\t:\t",sol[i],"\n")
}
```

## Q3. Writing the function

The dedicate_g3 function will construct a portfolio for any set of liabilities and bonds. The function takes four inputs: P, C, M, and L. P is the vector containing the prices of the bonds. C is the vector containing the coupon payments for the bonds. M is the vector containing the maturity (in years) for the bonds. Finally, L is the vector of non-negative liabilities for each year. The function outputs the optimal number of each bond to purchase to minimize price of bonds

```{r}
dedicate_g3 <- function(P,C,M,L){
  #Objective
  c = P
  
  #Constraints
  #Initialize constraints matrix with zeros
  A = matrix(0,length(L), length(C))
  
  for (i in seq_along(C)){
    A[1:M[i]-1,i] = C[i]
    
    #Matrix with maturity and final coupon payments
    A[M[i],i] = 100 + C[i]
  }
  
  #Direction
  dir = rep("=",length(L))
  
  #Constraints Vector
  b = L
  
  #Solution
  s = lp("min",c,A,dir,b,compute.sens=1)
  return(s)
}
```

Let's test the function using our test case from problem 2.

```{r}
#Inputs
#Liabilities
l = c(12000,18000,20000,20000,16000,15000,12000,10000)

#Bond prices
p = c(102,99,101,98,98,104,100,101,102,94)

#Coupons
coup = c(5,3.5,5,3.5,4,9,6,8,9,7)

#Maturities
m = c(1,2,2,3,4,5,5,6,7,8)

#Calling the function
s = dedicate_g3(p,coup,m,l)
sol = s$solution

#Optimal Solution
for (i in seq_along(sol)){
  cat("Bond",i,"\t:\t",sol[i],"\n")
}
```

The results match! 

## Q4. Construct a dedicated portfolio

Bond information was collected from the Wall Street Journal (http://online.wsj.com/mdc/public/page/2_3020-treasury.html#treasuryB) and stored as a csv file named "TreasuryQuotes_wsj.csv".

```{r}
#Reading bond information
Bonds = read.csv("TreasuryQuotes_wsj.csv")
```

Create input vectors

```{r}
#Limit bonds to only those that mature/pay coupons at the end of June/December
dates = c("6/30/2017","12/31/2017","6/30/2018","12/31/2018","6/30/2019","12/31/2019","6/30/2020","12/31/2020","6/30/2021","12/31/2021","6/30/2022","12/31/2022")

Bonds = Bonds[Bonds$Maturity %in% dates,]

#Price Vector
P = Bonds$Asked

#Coupon Vector
C = Bonds$Coupon/2

#Maturities Vector (in periods/half-years)
#Assign each date to period number
periods = seq_along(dates)
names(periods) = dates

#Initialize maturities vector with zeros
M = rep(0,length(Bonds$Maturity))

#Add period number corresponding to each maturity date to maturities vector
for (i in seq_along(M)){
  date = toString(Bonds$Maturity[i])
  period = periods[date]
  
  M[i] = period
}

#Non-negative liabilities vector
L = 1000000*c(9,9,10,10,6,6,9,9,10,10,5,3)
```

Finally, we can solve for the optimal amount of each bond to purchase using the function we defined in Q3.

```{r}
options("scipen"=100, "digits"=4)
#Calling the function
s = dedicate_g3(P,C,M,L)

optimal_solution = data.frame(Bonds$Maturity,Bonds$Coupon,Bonds$Asked,s$solution)
names(optimal_solution) = c("Maturity","Coupon","Price","Amount to Purchase")
optimal_solution
```

### Sensitivity Analysis
Next we can evaluate the sensitivity of this model to the liability constraints.

```{r}
optimal_sol_sens = data.frame(dates,L,s$duals[0:length(L)],s$duals.from[0:length(L)],s$duals.to[0:length(L)])
names(optimal_sol_sens) = c("Date","Liability","Duals","Duals From","Duals To")

optimal_sol_sens
```

```{r}
plot(periods, optimal_sol_sens$Duals, main="Liability Constraint Sensitivities Over Time", xlab="Liability Date", ylab="Duals", type='o', col='blue', xaxt='n')
axis(1, at=1:12, labels=dates[1:12])
```

The duals (i.e. sensitivity of the constraint for each half-year) can be interperted as the time value of money. In other words,  1 dollar on 12/31/2022 is worth 88 cents today. The Duals From & To are the range of liabilities for that date for which the duals/sensitivity applies.
